Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-30 thesis/acm/paper.tex
Added 1 more category, first page

\category{K.6.3}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]

>>>>

\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
\category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
